Handling String-Number Conversion in String Constraint Solving

### 2019-11-08 draft.tex
add an introduction paragraph for underapproximation

An \emph{equality constraint} $\phi_e$ is of the form $t_1 = t_2$ where $t_1, 
t_2$ are terms in $(\vars\cup \Sigma)^*$. The \emph{model} of $\phi_e$ is the set of interpretations $\modelsof{\phi_e}=\{I\mid 
I(t_1)=I(t_2)\}$. A \emph{disequality constraint} is of the form $t_1 \neq 
t_2$ and is interpreted analogously.

@@

@@

A \emph{string constraint} $\phi$ is in the form of $\bigwedge_{\pi \in \Pi} \pi$, where $\Pi$ is a set of the above three kinds of constraints. We say that $\phi$ is \emph{satisfiable}  iff $\bigcap_{\pi \in \Pi} \modelsof{\pi}$ is not empty.

@@

\section{Under-approximation}

>>>>

An \emph{equality constraint} $\phi_e$ is of the form $t_1 = t_2$ where $t_1, 
t_2$ are terms in $(\vars\cup \Sigma)^*$. The \emph{model} of $\phi_e$ is the set of interpretations $\modelsof{\phi_e}=\{I\mid 
I(t_1)=I(t_2)\}$. A \emph{disequality constraint} $\phi_d$ is of the form $t_1 \neq 
t_2$ and is interpreted analogously.

@@

A \emph{membership constraint} $\phi_m$ is of the form $x \in L(A)$ where $x$ is a string variable and $A$ is a finite automaton. The \emph{model} of $\phi_m$ is the set of interpretations $\modelsof{\phi_m}=\{I\mid 
I(x) \in L(A) \}$.

@@

A \emph{string constraint} is a constraint of the above form. We say that a set of string constraint $\phi$ is \emph{satisfiable}  iff $\bigcap_{\pi \in \phi} \modelsof{\pi}$ is not empty.

@@

\section{Under-approximation}
In this section, we describe formally how to restrict the domain of string variables to patterns defined by \emph{parametric flat automata} (PFA) (Section~\ref{section:sfa}) and hence convert string constraints $\phi_s$ to a set of equisatisfiable linear integer constraints $\phi_I$ in polynomial-time. We first pick a PFA for each variable in $\vars$ and then construct the set of linear integer constraints in a stepwise manner. In each step, we take a string constraint from $\phi_s$ and depending on the type of the string constraint, we execute the corresponding procedure to produce the linear integer constraints. The procedure for equality, disequality, and membership constraints is in Section~\ref{section:eq} and the one for string/integer conversion is in Section~\ref{section:s2i}.

\yfc{say handling membership constraint can be exponential to the number of constraints, but in our under-approximation, it is polynomial.}
